From Freebase to Wikidata: The Great Migration

### 2016-01-29 paper.tex
Reworked Section 3.3.

The data quality of Freebase was discussed by the Wikidata community, and it
was decided that the quality overall was not sufficient for a~direct import.
For example, a~small city in France was assigned an ISO country code,%
\footnote{Freebase topic page of the city of Saint-Martin: \url{http://www.freebase.com/m/03cc0d0}}
then Boston (the city in Massachusetts) had the type \texttt{/people/person},
and several other occurrences of data quality issues were revealed.
In consequence, a~fully automatic upload of all the content from Freebase into Wikidata
did not seem advisable as the expectations of the Wikidata community regarding the
quality of automatically uploaded data are high (and rightly so).
Despite the fact that an automated upload of all the data
would have led to accelerated growth in the short term,
such a~fast increase of available data would certainly have endangered
the sense of ownership of the Wikidata community for its data.
As an alternative approach, we decided to rely on crowdsourced human curation
and created the \emph{Primary Sources Tool},
a~widget that displays Freebase statements
for curation by the contributor that can be added to the currently shown Wikidata item.
The tool will be described in more detail in \autoref{sec:primary-sources-tool}.

>>>>

The data quality of Freebase was discussed by the Wikidata community, and it
was decided that the quality overall was not sufficient for a~direct import.
For example, a~small city in France was assigned an ISO country code,%
\footnote{Freebase topic page of the city of Saint-Martin: \url{http://www.freebase.com/m/03cc0d0}}
Boston (the city in Massachusetts) had the type \texttt{/people/person},
and several other occurrences of data quality issues were revealed.
In consequence, a~fully automatic upload of all the content from Freebase into Wikidata
did not seem advisable as the expectations of the Wikidata community regarding the
quality of automatically uploaded data are high (and rightly so).
Despite the fact that an automated upload of all the data
would have led to accelerated growth in the short term,
such a~fast increase of available data would certainly have endangered
the sense of ownership of the Wikidata community for its data.
As an alternative approach, we decided to rely on crowdsourced human curation
and created the \emph{Primary Sources Tool},
a~widget that displays Freebase statements
for curation by the contributor that can be added to the currently shown Wikidata item.
The tool will be described in more detail in \autoref{sec:primary-sources-tool}.
